\ldots

### 2016-02-04 paper.tex
Typo

To answer this study we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714} and three compositional datasets: KS14 \cite{kartsadrqpl2014}, GS11 \cite{Grefenstette:2011:ESC:2145432.2145580} and PhraseRel.

%\bibliographystyle{acl}
% remove publisher, month etc from conf proceedings:
\bibliographystyle{acl-short}
% \bibliographystyle{naaclhlt2016}
% \balance
\bibliography{references,dmilajevs_publications}

>>>>

To answer these questions we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714} and three compositional datasets: KS14 \cite{kartsadrqpl2014}, GS11 \cite{Grefenstette:2011:ESC:2145432.2145580} and PhraseRel.

%\bibliographystyle{acl}
% remove publisher, month etc from conf proceedings:
\bibliographystyle{acl-short}
% \bibliographystyle{naaclhlt2016}
\balance
\bibliography{references,dmilajevs_publications}
